\documentclass{article}
\usepackage{fullpage}
\usepackage[pdftex]{hyperref}

\thispagestyle{empty}
\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	


\begin{document}

\begin{changemargin}{-0.5in}{-0.5in} {\textbf{\Large Avanti Shrikumar}} \hfill \small{email me for address/phone $\vert$ avanti@cs.stanford.edu } \end{changemargin}
                                                                                                                                                           
\vspace*{.05in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\small{\vspace{17pt}
	\textbf{Stanford University}\hfill \emph{Sep 2014 - present} \\
	\begin{itemize}
	   \item PhD in Computer Science under Professor Anshul Kundaje \\
	\end{itemize}
	\textbf{Massachusetts Institute of Technology}\hfill \emph{June 2013} \\
	\begin{itemize}
	   \item B.S. Computer Science with Molecular Biology, Minor in Mathematics \hfill \emph{GPA 5.0/5.0} \\
	\end{itemize}}
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Experience}

\begin{body}
	\small{\vspace{17pt}
	\textbf{Palantir Technologies Healthcare Team} - \emph{Forward Deployed Engineer} \hfill \emph{June 2013 - Sep 2014} \\
   \begin{itemize}
           \item Primary developer for team's first enterprise deployment. Created a way to integrate Palantir's two major platforms into a seamless experience; success was highlighted company-wide. Built multiple code libraries off-the-clock for use team-wide and company-wide; 3 ongoing patent filings/discussions.
           \item Consistently rated high on bi-annual reviews, in which lead (Lekan Wang) told me I had at times done the work of 2-3 coders and had set a new standard for productivity among my teammates.
   \end{itemize}
	\textbf{MIT Computational Biology Group (Kellis Lab)} - \emph{SuperUROP} \hfill \emph{Sep 2012 - June 2013} \\
   \begin{itemize}
           \item Without supervision of a graduate student, applied a Hidden Markov Model to identify transcription factor binding sites using histone modification data. Won an award for outstanding research.
   \end{itemize}
	\textbf{MIT Boyer Lab} - \emph{UROP} \hfill \emph{Sep 2010 - Sep 2012} \\
   \begin{itemize}
           \item Analyzed high-throughput data on cardiac stem cells.  Exercised autonomy on how best to process the data to answer biological questions. As I matured as a researcher, I tested my own hypotheses and presented results to my Postdoctoral colleague. See publication.
                 Supervisors: Professor Laurie Boyer, Dr. Joseph Wamstad.
   \end{itemize}}
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%PUBLICATION

\header{Publications}

\begin{body}
	\small{
	\vspace{17pt}
	\textbf{Cell} -  \emph{Sep 2012} \\
   \begin{itemize}
   	   \item Collaboration between Boyer lab at MIT and Gladstone Institute. I performed the bulk of bioinformatics analysis at the Boyer lab. \href{http://www.ncbi.nlm.nih.gov/pubmed/22981692}{\bf Dynamic and coordinated epigenetic regulation of developmental transitions in the cardiac lineage}.
	  Cell 151, 206-220.\\
	  \item 104 citations as of Sep 2014.   
   \end{itemize}
	\textbf{Circulation Research} -  \emph{Dec 2014} \\
   \begin{itemize}
   	   \item Collaboration between Boyer lab at MIT and Lee lab at Harvard. I analysed RNA-seq data to study transcriptional reversion. \href{http://www.ncbi.nlm.nih.gov/pubmed/25477501}{\bf Transcriptional Reversion of Cardiac Myocyte Fate During Mammalian Cardiac Regeneration}. Circ Res. 2014 Dec 4. pii: CIRCRESAHA.114.304269. 
   \end{itemize}
   
   }
   
\end{body}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skillz
\header{Skills}

\begin{body}
	\small{
	\vspace{17pt}
	\textbf{Programming}
	\begin{itemize}
	      \item Primary languages: Java (primary language at Palantir), Python (primary language during PhD; personal emphasis on code reusability in contrast to `hacky' culture of bioinformatics), Perl (for ``quick and dirty'')
		  \item VPython: Personal coding projects in high school. Simulations of Rubik's Cube and Sudokube: \href{http://www.youtube.com/watch?v=fLvs5nvT2j8}{http://www.youtube.com/watch?v=fLvs5nvT2j8}
		  \item Moderate experience in SQL/PostgreSQL, Javascript/CSS/HTML, R and MATLAB.
	\end{itemize}
	\textbf{Interesting}
	\begin{itemize}
	      \item Calculator art with parametric equations \href{http://www.youtube.com/watch?v=r-I5M--fvJQ}{http://www.youtube.com/watch?v=r-I5M-\--fvJQ})
	      \item Acted in multiple student theater productions at MIT, directed for one.
	\end{itemize}
	}
\end{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards
\header{Achievements \& Honors}

\begin{body}
	  \small{	  
	  \vspace{17pt}
	   \textbf{SuperUROP Outstanding Research Award}
	    \begin{itemize}
	     \item For project ``Doubling the precision of DNA binding site prediction using a novel dataset" in Kellis lab
	    \end{itemize}
	  \textbf{American Institute of Chemical Engineers Sophomore Academic Excellence Award}
	    \begin{itemize}
	     \item Awarded to the student with the highest GPA among chemical engineering sophomores at MIT. 
	    \end{itemize}
	  \textbf{IGCSE examinations}
	    \begin{itemize}
	     \item The IGCSE was administered in roughly 300 schools in India. I had the highest score in India in Extended Mathematics Without Coursework (June 2006), Physics(June 2007) and Geography (June 2007).
	    \end{itemize}
 	   }
\end{body}
\end{document}
